---
title: "Results Summary"
output: html_document
---

#### --> e.g., check spatial compatibility of different reduced spatial coverage approaches
### -> also see predictions inside monitoring area and outside (how far out can u predict?)

### --> ?	estimate performance statistics using the observations from our full campaign as the reference (gold standard)

### -> are prediction errors worse at some places with reduced sampling (e.g., airport?)

### --> ? prediciton models (?ANOVA) looking at what impacts MSE the most?


```{r}
pacman::p_load(knitr, kableExtra, broom,
               ggpubr, tidyverse,
               ggrepel, #geom_label_repel
               ggmap, sf, ggspatial, #mapping...adding scales, N arrows
               ggrepel, #avoid overlapping labels
               units, #convert between e.g., m to km
               #time series data 
               lubridate,
               
               fmsb, #percentile()
               GGally, #ggpairs()
               VCA #anovaVCA()
               )    
 

# ggplot settings
theme_set(theme_bw())
theme_update(legend.position = "bottom")

##boxplot outlier
outlier_size <- 0.7
outlier_alpha <- 0.4

source("0_functions.R")

set.seed(1)
```

# Stops used

range of times used for calculating annual averages; number of stops; check that temporal balance remains after dropping initial stops

```{r}

```


# Summary of simulation designs

e.g., for each design: description, range of # visits used, # stops used, 

```{r}

```



# Annual averages 

compare annual averages from temporal simulations 

```{r}

```

# covariates used in models

n?

```{r}

```


# Clustered/Validation Sets

show clustered validation groups; including routes

show diff sets: e.g., test, validation, "out-of-region"

```{r}


```


# Predictions

```{r}

```


Kriging has an assumption of normally distributed residuals. log transform if these are not normally distributed. 

### --> ? *look at distribution of residuals at 280 sites after subtracting regression part 


```{r}

```



# Model Performances

RMSE, error, R2..


```{r}


```



# Maps/plots of prediction differences

how to predictions change across designs? 


```{r}

```


